Probability Aggregation: Dynamic Hierarchical Modeling of Sparse Expert Beliefs

### 2013-08-31 paper.tex
Edits

The data collection began with recruitment of 2,365 forecasters ranging from graduate students to political science faculty and practitioners. The recruiting was made from professional societies, research centers, alumni associations, science bloggers, and word of mouth. Requirements included at least a Bachelor's degree and completion of psychological and political tests that took roughly two hours. These measures assessed cognitive styles, cognitive abilities, personality traits, political attitudes, and real-world knowledge. The experts were asked to give probability forecasts (to the second decimal point) and to self-assess their level of expertise (on a 1-to-5 scale with 1 = Not At All Expert and 5 = Extremely Expert) on a number of 166 geopolitical binary events taking place between September 29, 2011 and May 8, 2013. Each question was active for a period of time during which the participating experts were allowed to update their forecasts as frequently as they liked without being penalized. The forecasters knew that their probability estimates would be assessed for accuracy using Brier scores\footnote{The Brier score is the squared distance between the probability forecast and the event indicator that equals 1.0 or 0.0 depending on whether the event happened or not, respectively. See \citet{Brier} for the original introduction.}. This incentivized them to report their true beliefs instead of attempting to game the system (\citet{winkler1968good}). In addition to receiving \$150 for meeting minimum participation requirements that did not depend on prediction accuracy, the forecasters also received status rewards for their performance via leader-boards displaying Brier scores for the top 20 forecasters. Since a typical expert participated only in a small subset of the 166 questions, the forecasters are considered indistinguishable conditional on the level of self-reported expertise.
Tables \ref{DataStats} and \ref{ExpertiseTable} provide more relevant summary statistics on the data. Notice that the distribution of the self-reported expertise is skewed to the right and that some questions remained active longer than others.  For more details on the data and its collection see \citet{ungar2012good}.

@@

To illustrate the nature of the data with some concrete examples, Figures \ref{Example1} and \ref{Example2} show scatterplots of the probability forecasts given for (a) \textit{Will the expansion of the European bailout fund be ratified by all 17 Eurozone nations before 1 November 2011?}, and (b) \textit{Will the Nikkei 225 index finish trading at or above 9,500 on 30 September 2011?}. The points have been jittered slightly to make overlaps visible. The darkness of the points is positively associated with the self-reported expertise. Given that the European bailout fund was ratified before 1 November 2011 and that the Nikkei 225 index finished trading at around 8,700 on 30 September 2011, the general trend of the probability forecasts converge to the correct answers. There is, however, much disagreement among the experts. This disagreement persists even near the closing dates of the questions. Unfortunately, the data is not only noisy but also quite sparse. As mentioned before, the forecasters were allowed to update their forecast as long as the questions remained open. Updating, however, was done on a very infrequent basis. An expert gave, on average, only 0.016 forecasts per day, and so a typical expert made a forecast about every 62 days. As a result the average response rate was around 13.5 forecasts per day from a large group of experts.

\section{Model}
\label{model}
Let $p_{i,t,k} \in (0,1)$ be the probability forecast given by the $i$th expert at time $t$ for the $k$th question, where $i = i, \dots, I_k$, $t = 1, \dots, T_k$, and $k = 1, \dots, K$. Denote the logit-probabilities with 
\begin{eqnarray*}
Y_{i,t,k} = \logit(p_{i,t,k}) = \log \left( \frac{p_{i,t,k}}{1-p_{i,t,k}}\right) \in \R
\end{eqnarray*}
and collect the logit-probability forecasts given for question $k$ at time $t$ into a vector $\boldsymbol{Y}_{t,k} = [Y_{1,t,k}\ Y_{2,t,k}\ \dots\ Y_{I_{k},t,k}]^T$. Partition the experts into $J$ groups based on some individual feature, such as self-reported expertise, with each group sharing a common multiplicative bias term $b_{j} \in \R$ for $j = 1, \dots, J$. Collect these bias terms into a bias vector $\boldsymbol{b} = [b_{1}\ b_{2}\ \dots\ b_{J}]^T$ and let $\boldsymbol{M}_k$ be a $I_k \times J$ matrix denoting  the group-memberships of the forecasters in question $k$. That is, if the $i$th expert participating in the $k$th question belongs to the $j$th group, then the $i$th row of $\boldsymbol{M}_k$ is the $j$th standard basis vector, $\boldsymbol{e}_j$. The bias vector $\boldsymbol{b}$ does not include a subindex because it is considered shared among all the $K$ questions. To secure model identifiability, it is sufficient to share only one of the elements of $\boldsymbol{b}$ among the questions. This element defines a baseline under which it is possible to estimate the remaining $J-1$ bias terms separately within each of the questions. In this paper, however, the entire vector $\boldsymbol{b}$ is shared because some of the questions in our real-world data set involve very few experts with the highest level of self-reported expertise. Under this notation, the model for the $k$th question can be expressed as 
\begin{eqnarray}
\boldsymbol{Y}_{t, k} &=&  \boldsymbol{M}_k \boldsymbol{b} X_{t, k} + \boldsymbol{v}_{t, k} \label{observedpr} \\
X_{t, k} &=& \gamma_k X_{t-1, k} + w_{t, k} \label{hiddenpr}\\
X_{0,k} &\sim& \mathcal{N}(\mu_0, \sigma^2_0) \nonumber
\end{eqnarray}
where Equation (\ref{observedpr}) denotes the observed process, Equation (\ref{hiddenpr}) shows the hidden process that is driven by the constant $\gamma_k \in \R$. The error terms are independent and identically distributed normal random variables with mean zero
\begin{eqnarray*}
\boldsymbol{v}_{t, k} | \sigma^2_k &\stackrel{i.i.d.}{\sim}& \mathcal{N}_{I_k}(\boldsymbol{0}, \sigma^2_k \boldsymbol{I}_{I_k})\\
w_{t, k} | \tau^2_k &\stackrel{i.i.d.}{\sim}& \mathcal{N}(0, \tau^2_k),
\end{eqnarray*}
and $(\mu_0, \sigma_0^2) \in (\R, \R^+)$ are hyper-parameters chosen \textit{a priori}. The hidden state $X_{t,k}$ represents the sharp and calibrated logit-probability for the $k$th event given the information available up to and including time $t$. To make this more specific, let $Z_k \in \{0, 1\}$ indicate whether the event associated with the $k$th question happened $\left(Z_k = 1\right)$ or did not happen $\left(Z_k = 0\right)$. If $\{\mathcal{F}_{t,k}\}_{t=1}^{T_k}$ is a filtration representing the information available up to and including a given time point, then $\E[Z_k | \mathcal{F}_{t,k}] = \P(Z_k = 1| \mathcal{F}_{t,k}) = \logit^{-1}(X_{t,k})$. These probabilities are made estimable by assuming that the observed process is associated with the filtration $\{\mathcal{F}_{t,k}\}_{t=1}^{T_k}$ and hence can be used as a proxy for the amount of information available at any given time point. Therefore it is not unreasonable to interpreted the hidden process as the crowd belief across time.

@@

\subsection{Sampling Step}
\label{sampling_step}
Since $\left(a \boldsymbol{b}, X_{t,k}/a, a^2 \tau_k^2\right) \neq \left(\boldsymbol{b}, X_{t,k}, \tau_k^2\right)$ for any $a > 0$ yield the same  likelihood for $\boldsymbol{Y}_{t,k}$, the model as described by Equations (\ref{observedpr}) and (\ref{hiddenpr}) is not identifiable and the parameter estimates tend to drift during the sampling process. A well-known solution is to choose one of the elements of $\boldsymbol{b}$, say $b_3$, as the reference point and fix $b_3 = 1$.  Denote the constrained version of the model by
\begin{eqnarray*}
\boldsymbol{Y}_{t, k} &=&  \boldsymbol{M}_k \boldsymbol{b} (1) X_{t, k}(1)+ \boldsymbol{v}_{t, k}\\
X_{t, k}(1) &=& \gamma_k(1) X_{t-1, k}(1) + w_{t, k}\\
\boldsymbol{v}_{t, k} | \sigma^2_k(1) &\stackrel{i.i.d.}{\sim}& \mathcal{N}_{I_k}(\boldsymbol{0}, \sigma^2_k(1) \boldsymbol{I}_{I_k})\\
w_{t, k} | \tau^2_k(1) &\stackrel{i.i.d.}{\sim}& \mathcal{N}\left(0, \tau^2_k(1)\right),
\end{eqnarray*}
where the trailing input parameter emphasizes the constraint $b_{3} = 1$. Since this version is identifiable, estimates of the model parameters can be obtained. Denote the estimates by placing a hat on the parameter symbol. For instance, $\hat{\boldsymbol{b}}(1)$ and $\hat{X}_{t, k}(1)$ represent the estimates of $\boldsymbol{b}(1)$ and $X_{t, k}(1)$, respectively. These estimates are found via a Gibbs sampler that only makes use of standard distributions. See Appendix \ref{appendix} for the technical details of our sampler, and, e.g., \citet{gelman2003bayesian} for a discussion on the general principles of Gibbs sampling.

@@

The synthetic data is not generated directly from the model for two reasons: (i) showing good performance on a dataset directly generated from the model assumptions is hardly any news, and (ii) generating data from the dynamic model description does not produce well-calibrated hidden states. The latter is important for our interpretation of the hidden states as a sharp and well-calibrated versions of the crowd belief. To generate a well-calibrated hidden process, generate a path of the standard Brownian motion until time $T_k$ for question $k$, and let $Z_{t,k}$ denote the value of the path at time $t$. Then, for $t = 1, \dots, T_k$,
\begin{eqnarray*}
Z_k &=& \mathbbm{1}\left( Z_{T_k, k}  > 0\right)\\
 X_{t,k} &=& \logit \left[ \Phi \left(\frac{Z_{t, k}}{\sqrt{T_k- t}} \right) \right]
\end{eqnarray*}
gives a sequence of $T_k$ calibrated logit-probabilities for the event $Z_k = 1$.

We used this procedure to generate the hidden processes for $K$ questions with $T_k = 100$. Each question involved 50 experts allocated evenly among the five expertise groups. Their reported logit-probabilities, $Y_{t,k}$, were generated from Equation (\ref{observedpr}) by applying bias and noise to the hidden process. Similarly to the real-world data setting discussed in Section \ref{realData}, extreme logit-probabilities are truncated to avoid overly influential observations; that is, any $p_{i,t,k} = \logit^{-1}(Y_{i,t,k})$ less than 0.01 (or greater than 0.99) is truncated to 0.01 (or to 0.99). The simulation was then performed over a three-dimensional grid of parameter values:
\begin{eqnarray*}
\beta &\in& \{1/2, 3/4, 1, 4/3, 2/1\}\\
\sigma^2 &\in& \{0.5, 1.0, 1.5, 2.0, 2.5\}\\
K &\in& \{20, 35, 50, 65, 80\},
\end{eqnarray*}
where $\beta$ generates the bias vector by  $\boldsymbol{b} = [0.50, 0.75, \dots, 1.50]^T \beta$. 
The simulation runs a total of 40 times at every grid point. Each run records the accuracy to which the approaches are able to estimate the hidden process and bias vector.

%The number of questions, $K$, varies between $20$ and $80$ with increments of 15 problems, the bias vector changes as $$\boldsymbol{b} = [0.50, 0.75, \dots, 1.50]^T \beta,$$ where $\beta$ takes values in $1/2, 3/4, 1, 4/3$, and $2/1$ symmetrically around 1 in the log-scale, and finally the values of $\sigma^2$ vary from $0.5$ to $2.0$ with increments of $0.5$.

Figure \ref{Synthetic} summarizes the results in a series of plots. The first row shows the marginal effects of the three grid variables on the accuracy to which the \textit{Sample-Then-Calibrate} under the logarithmic loss (STC-Log) and the Brier score (STC-Bri) are able to estimate the hidden process. The accuracy is measured in terms of the average quadratic loss in the probability space, $\sum_{k=1}^K \sum_{t=1}^{T_k} (\hat{p}_{t,k} - \logit^{-1}(X_{t,k}))^2 / \sum_{k=1}^K T_k$. The second row is similar in nature but measures the accuracy of estimating the bias vector instead. The accuracy is measured in terms of the average quadratic loss, $|| \boldsymbol{b} - \hat{\boldsymbol{b}}||^2/5$. The plots were computed by choosing one grid variable (e.g. $\beta$)  at a time and averaging over the remaining two variables  (e.g. $K$, and $\sigma^2$).  Therefore each value in the plots represents an average of a $40 \times 5^2 = 1,000$ values.

Based on the first row of plots, STC-Log and STC-Bri estimate the hidden process to a similar accuracy. Even though some relative differences are visible, the loss values are very small in absolute terms; hence suggesting good overall accuracy to capture the hidden process. While increasing the number of questions improves the accuracy to a small extent, estimating the hidden process becomes more difficult as either $\sigma^2$ or $\beta$ gets larger. The latter seems more unintuitive and can be understood better by observing that larger values of $\beta$ lead to more extreme expert logit-probabilities. As a result, more logit-probabilities are modified by truncation, leading to poorer estimation accuracy.

Based on the second row of plots, STC-Log and STC-Bri  capture the bias vector rather precisely as long as the true values of $\beta$ and $\sigma^2$ are not very large. This behavior can be considered as being caused  to a large extent by the truncation of the extreme expert logit-probabilities. Surprisingly, even though STC-Log is more accurate in estimating the bias vector, it is unable to outperform STC-Bri in estimating the hidden process.

\begin{figure}[h!]
\vspace{-5em}
\centering
 \hspace{-30em}	\includegraphics{Figures/LegendSynthetic} % requires the graphicx package
\vspace{-0.5em}

@@

@@

>>>>

The data collection began with a recruitment of 2,365 forecasters ranging from graduate students to political science faculty and practitioners. The recruiting was made from professional societies, research centers, alumni associations, science bloggers, and word of mouth. Requirements included at least a Bachelor's degree and completion of psychological and political tests that took roughly two hours. These measures assessed cognitive styles, cognitive abilities, personality traits, political attitudes, and real-world knowledge. The experts were asked to give probability forecasts (to the second decimal point) and to self-assess their level of expertise (on a 1-to-5 scale with 1 = Not At All Expert and 5 = Extremely Expert) on a number of 166 geopolitical binary events taking place between September 29, 2011 and May 8, 2013. Each question was active for a period of time during which the participating experts were allowed to update their forecasts as frequently as they liked without being penalized. The forecasters knew that their probability estimates would be assessed for accuracy using Brier scores\footnote{The Brier score is the squared distance between the probability forecast and the event indicator that equals 1.0 or 0.0 depending on whether the event happened or not, respectively. See \citet{Brier} for the original introduction.}. This incentivized them to report their true beliefs instead of attempting to game the system (\citet{winkler1968good}). In addition to receiving \$150 for meeting minimum participation requirements that did not depend on prediction accuracy, the forecasters also received status rewards for their performance via leader-boards displaying Brier scores for the top 20 forecasters. Since a typical expert participated only in a small subset of the 166 questions, the forecasters are considered indistinguishable conditional on the level of self-reported expertise.
Tables \ref{DataStats} and \ref{ExpertiseTable} provide more relevant summary statistics on the data. Notice that the distribution of the self-reported expertise is skewed to the right and that some questions remained active longer than others.  For more details on the data and its collection see \citet{ungar2012good}.

@@

To illustrate the nature of the data with some concrete examples, Figures \ref{Example1} and \ref{Example2} show scatterplots of the probability forecasts given for (a) \textit{Will the expansion of the European bailout fund be ratified by all 17 Eurozone nations before 1 November 2011?}, and (b) \textit{Will the Nikkei 225 index finish trading at or above 9,500 on 30 September 2011?}. The points have been jittered slightly to make overlaps visible. The darkness of the points is positively associated with the self-reported expertise. Given that the European bailout fund was ratified before 1 November 2011 and that the Nikkei 225 index finished trading at around 8,700 on 30 September 2011, the general trends of the probability forecasts converge to the correct answers. There is, however, much disagreement among the experts. This disagreement persists even near the closing dates of the questions. Unfortunately, the data is not only noisy but also quite sparse. As mentioned before, the forecasters were allowed to update their forecast as long as the questions remained open. Updating, however, was done on a very infrequent basis. An expert gave, on average, only 0.016 forecasts per day, and so a typical expert made a forecast about every 62 days. As a result the average response rate was around 13.5 forecasts per day from a large group of experts.

\section{Model}
\label{model}
Let $p_{i,t,k} \in (0,1)$ be the probability forecast given by the $i$th expert at time $t$ for the $k$th question, where $i = 1, \dots, I_k$, $t = 1, \dots, T_k$, and $k = 1, \dots, K$. Denote the logit-probabilities with 
\begin{eqnarray*}
Y_{i,t,k} = \logit(p_{i,t,k}) = \log \left( \frac{p_{i,t,k}}{1-p_{i,t,k}}\right) \in \R
\end{eqnarray*}
and collect the logit-probability forecasts given for question $k$ at time $t$ into a vector $\boldsymbol{Y}_{t,k} = [Y_{1,t,k}\ Y_{2,t,k}\ \dots\ Y_{I_{k},t,k}]^T$. Partition the experts into $J$ groups based on some individual feature, such as self-reported expertise, with each group sharing a common multiplicative bias term $b_{j} \in \R$ for $j = 1, \dots, J$. Collect these bias terms into a bias vector $\boldsymbol{b} = [b_{1}\ b_{2}\ \dots\ b_{J}]^T$ and let $\boldsymbol{M}_k$ be a $I_k \times J$ matrix denoting  the group-memberships of the forecasters in question $k$. That is, if the $i$th expert participating in the $k$th question belongs to the $j$th group, then the $i$th row of $\boldsymbol{M}_k$ is the $j$th standard basis vector, $\boldsymbol{e}_j$. The bias vector $\boldsymbol{b}$ does not include a subindex because it is considered shared among all the $K$ questions. To secure model identifiability, it is sufficient to share only one of the elements of $\boldsymbol{b}$ among the questions. This element defines a baseline under which it is possible to estimate the remaining $J-1$ bias terms separately within each of the questions. In this paper, however, the entire vector $\boldsymbol{b}$ is shared because some of the questions in our real-world data set involve very few experts with the highest level of self-reported expertise. Under this notation, the model for the $k$th question can be expressed as 
\begin{eqnarray}
\boldsymbol{Y}_{t, k} &=&  \boldsymbol{M}_k \boldsymbol{b} X_{t, k} + \boldsymbol{v}_{t, k} \label{observedpr} \\
X_{t, k} &=& \gamma_k X_{t-1, k} + w_{t, k} \label{hiddenpr}\\
X_{0,k} &\sim& \mathcal{N}(\mu_0, \sigma^2_0) \nonumber
\end{eqnarray}
where Equation (\ref{observedpr}) denotes the observed process, Equation (\ref{hiddenpr}) shows the hidden process that is driven by the constant $\gamma_k \in \R$. The error terms are independent and identically distributed normal random variables with mean zero
\begin{eqnarray*}
\boldsymbol{v}_{t, k} | \sigma^2_k &\stackrel{i.i.d.}{\sim}& \mathcal{N}_{I_k}(\boldsymbol{0}, \sigma^2_k \boldsymbol{I}_{I_k})\\
w_{t, k} | \tau^2_k &\stackrel{i.i.d.}{\sim}& \mathcal{N}(0, \tau^2_k),
\end{eqnarray*}
and $(\mu_0, \sigma_0^2) \in (\R, \R^+)$ are hyper-parameters chosen \textit{a priori}. The hidden state $X_{t,k}$ represents the sharp and well-calibrated logit-probability for the $k$th event given the information available up to and including time $t$. To make this more specific, let $Z_k \in \{0, 1\}$ indicate whether the event associated with the $k$th question happened $\left(Z_k = 1\right)$ or did not happen $\left(Z_k = 0\right)$. If $\{\mathcal{F}_{t,k}\}_{t=1}^{T_k}$ is a filtration representing the information available up to and including a given time point, then $\E[Z_k | \mathcal{F}_{t,k}] = \P(Z_k = 1| \mathcal{F}_{t,k}) = \logit^{-1}(X_{t,k})$. These probabilities are made estimable by assuming that the observed process is associated with the filtration $\{\mathcal{F}_{t,k}\}_{t=1}^{T_k}$ and hence can be used as a proxy for the amount of information available at any given time point. 
%Therefore it is not unreasonable to interpreted the hidden process as the crowd belief across time.

@@

\subsection{Sampling Step}
\label{sampling_step}
Since $\left(a \boldsymbol{b}, X_{t,k}/a, a^2 \tau_k^2\right) \neq \left(\boldsymbol{b}, X_{t,k}, \tau_k^2\right)$ for any $a > 0$ yield the same  likelihood for $\boldsymbol{Y}_{t,k}$, the model as described by Equations (\ref{observedpr}) and (\ref{hiddenpr}) is not identifiable and the parameter estimates tend to drift during the sampling process. A well-known solution is to choose one of the elements of $\boldsymbol{b}$, say $b_3$, as the reference point and fix $b_3 = 1$.  Denote the constrained version of the model by
\begin{eqnarray*}
\boldsymbol{Y}_{t, k} &=&  \boldsymbol{M}_k \boldsymbol{b} (1) X_{t, k}(1)+ \boldsymbol{v}_{t, k}\\
X_{t, k}(1) &=& \gamma_k(1) X_{t-1, k}(1) + w_{t, k}\\
\boldsymbol{v}_{t, k} | \sigma^2_k(1) &\stackrel{i.i.d.}{\sim}& \mathcal{N}_{I_k}(\boldsymbol{0}, \sigma^2_k(1) \boldsymbol{I}_{I_k})\\
w_{t, k} | \tau^2_k(1) &\stackrel{i.i.d.}{\sim}& \mathcal{N}\left(0, \tau^2_k(1)\right),
\end{eqnarray*}
where the trailing input parameter emphasizes the constraint $b_{3} = 1$. Since this version is identifiable, estimates of the model parameters can be obtained. Denote the estimates by placing a hat on the parameter symbol. For instance, $\hat{\boldsymbol{b}}(1)$ and $\hat{X}_{t, k}(1)$ represent the estimates of $\boldsymbol{b}(1)$ and $X_{t, k}(1)$, respectively. These estimates are found via Gibbs sampling that only makes use of standard distributions. See Appendix \ref{appendix} for the technical details of our sampler, and, e.g., \citet{gelman2003bayesian} for a discussion on the general principles of Gibbs sampling.

@@

The synthetic data is not generated directly from the model for two reasons: (i) showing good performance on a dataset directly generated from the model assumptions is hardly any news, and (ii) generating data from the dynamic model description does not produce well-calibrated hidden states. The latter is important for our interpretation of the hidden process as a sharp and well-calibrated version of the crowd belief. To ensure that the hidden process for question $k$ is well-calibrated, generate a path of the standard Brownian motion until time $T_k$. If $Z_{t,k}$ denotes the value of the path at time $t$, then
\begin{eqnarray*}
Z_k &=& \mathbbm{1}\left( Z_{T_k, k}  > 0\right)\\
 X_{t,k} &=& \logit \left[ \Phi \left(\frac{Z_{t, k}}{\sqrt{T_k- t}} \right) \right]
\end{eqnarray*}
gives a sequence of $T_k$ calibrated logit-probabilities for the event $Z_k = 1$.

We use this procedure to generate the hidden processes for $K$ questions with $T_k = 100$ for $k = 1, \dots, K$. Each question involves 50 experts allocated evenly among the five expertise groups. The expert logit-probabilities $Y_{t,k}$ are generated from Equation (\ref{observedpr}) by applying bias and noise to the hidden process $X_{t,k}$. Similarly to the real-world data setting discussed in Section \ref{realData}, extreme logit-probabilities are truncated to avoid overly influential observations; that is, any $p_{i,t,k} = \logit^{-1}(Y_{i,t,k})$ less than 0.01 (or greater than 0.99) is truncated to 0.01 (or to 0.99).

The simulation is then performed over a three-dimensional grid of parameter values:
\begin{eqnarray*}
\beta &\in& \{1/2, 3/4, 1, 4/3, 2/1\}\\
\sigma^2 &\in& \{0.5, 1.0, 1.5, 2.0, 2.5\}\\
K &\in& \{20, 35, 50, 65, 80\},
\end{eqnarray*}
where $\beta$ generates the bias vector by  $\boldsymbol{b} = [0.50, 0.75, \dots, 1.50]^T \beta$. 
The simulation runs a total of 40 times at every grid point. Each run records the accuracy to which the approaches are able to estimate the hidden process and bias vector. The first is measured in terms of the average quadratic loss in the probability space, $\sum_{k=1}^K \sum_{t=1}^{T_k} (\hat{p}_{t,k} - \logit^{-1}(X_{t,k}))^2 / \sum_{k=1}^K T_k$, while the latter is measured in terms of the average quadratic loss, $|| \boldsymbol{b} - \hat{\boldsymbol{b}}||^2/5$.

\begin{figure}[h!]
\vspace{-5em}
\centering
 \hspace{-28em}	\includegraphics{Figures/LegendSynthetic} % requires the graphicx package
\vspace{-0.5em}

@@

\vspace{-1em}

@@

Figure \ref{Synthetic} summarizes the results in a series of plots. The first row shows the marginal effects of the three grid variables on the accuracy to which the \textit{Sample-Then-Calibrate} under the logarithmic loss (STC-Log) and the Brier score (STC-Bri) are able to estimate the hidden process.  The second row is similar in nature but measures the accuracy of estimating the bias vector instead.  The plots were computed by choosing one grid variable (e.g. $\beta$) at a time and averaging over the remaining two variables  (e.g. $K$, and $\sigma^2$).  Therefore each value in the plots represents an average of a $40 \times 5^2 = 1,000$ values.

Based on the first row of plots, STC-Log and STC-Bri estimate the hidden process to a similar accuracy. Even though some relative differences are visible, the loss values are very small in absolute terms; hence suggesting good overall accuracy to capture the hidden process. Estimating the hidden process, however, becomes more difficult as either $\sigma^2$ or $\beta$ gets larger. The latter seems more unintuitive and can be understood better by observing that larger values of $\beta$ lead to more extreme expert logit-probabilities and hence to more frequent truncation. This causes the estimation accuracy to degrade because  a high level of truncation results to a drastic deviation from the model assumptions.

Based on the second row of plots, STC-Log and STC-Bri  capture the bias vector rather precisely as long as the true values of $\beta$ and $\sigma^2$ are not very large. This behavior can be again considered as being caused  to a large extent by the truncation of the extreme expert logit-probabilities. Surprisingly, even though STC-Log is more accurate in estimating the bias vector, it is unable to outperform STC-Bri in estimating the hidden process.
